---
title: "CHS - Model Revisions"
author: "Abigail Seeger"
date: "7/1/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, message = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
```

Read in the data. 

```{r}
CHS_data <- read.csv("~/LA's BEST/CHS_Poster/CHS_cohortE_final_subset.csv")
```

Convert the necessary columns to be factors.

```{r}
CHS_data$asthma <- factor(CHS_data$asthma, levels = c(0, 1), labels = c("No Asthma", "Asthma"))
CHS_data$hisp <- factor(CHS_data$hisp)
CHS_data$townabbr <- factor(CHS_data$townabbr)
CHS_data$sex <- factor(CHS_data$male, levels = c(0, 1), labels = c("Female", "Male"))
CHS_data$educ <- factor(CHS_data$educ, levels = c(1, 2, 3, 4, 5), labels = c("No HS", "HS", "Some College", "4-Year Degree", "Some post-graduate"))
CHS_data$wheeze <- factor(CHS_data$wheeze, levels = c(0, 1), labels = c("No Wheeze", "Wheeze"))
CHS_data$obesity <- factor(CHS_data$obesity, levels = c(TRUE, FALSE), labels = c("Obese", "Not Obese"))
```

Here is our initial final model:

```{r}
final_model <- lm(fev1 ~ factor(male) + age + factor(obesity)  + factor(townabbr) + pm25 + factor(educ) + factor(race), data = CHS_data)
final_model
```

Following Dr. Siegmund's advice, remove "townabbr" as a factor from the model:

Now sulfate is significant, but pm25 isn't. The direction makes sense now. 
So, we need to make a map of sulfate to include instead of pm25. 

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + sulfate + factor(educ) + factor(race), data = CHS_data)%>%summary()
## Hisp data
lm(fev1 ~ factor(male) + age + factor(obesity) + sulfate + factor(educ) + factor(race), data = filter(CHS_data, hisp == "Hispanic"))%>%summary()
### Non-hisp data
lm(fev1 ~ factor(male) + age + factor(obesity) + sulfate + factor(educ) + factor(race), data = filter(CHS_data, hisp == "Non-Hispanic"))%>%summary()
```
Now, here was our final asthma model:

```{r}
final_model <- glm(asthma ~ male + age + obesity + race + townabbr + educ  + ec, family = "binomial", data = CHS_data)
```

Per Dr. Siegmund's advice, remove townabbr.

```{r}
### Full model
glm(asthma ~ as.factor(male) + age + as.factor(obesity) + as.factor(race)  + ec + as.factor(educ) , family = "binomial", data = CHS_data)%>%summary()
### Hispanic model
glm(asthma ~ as.factor(male) + age + as.factor(obesity) + as.factor(race)  + ec + as.factor(educ) , family = "binomial", data = filter(CHS_data, hisp == "Hispanic"))%>%summary()
### Non-Hispanic model
glm(asthma ~ as.factor(male) + age + as.factor(obesity) + as.factor(race)  + ec + as.factor(educ) , family = "binomial", data = filter(CHS_data, hisp == "Non-Hispanic"))%>%summary()
```


```{r}
tiff("ModelDiagnostics2.tiff", units="in", width=5, height=5, res=500)
par(mfrow = c(2,2))
plot(lm(fev1 ~ factor(male) + age + factor(obesity) + sulfate + factor(educ) + factor(race), data = CHS_data))
dev.off()
```

