---
title: "CHS Regression"
author: "Abigail Seeger"
date: "6/24/2021"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r warning = FALSE, message = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
```


```{r}
CHS_data <- read.csv("~/LA's BEST/CHS_Poster/CHS_cohortE_final_subset.csv")
```

We are looking at the relationship between asthma and FEV1 for the entire dataset and by ethnicity.

First, build a simple model where ethnicity is the predictor variable and fev1 is the response variable. 

```{r}
### Convert the hisp column to a factor
CHS_data$hisp <- factor(CHS_data$hisp)
### Build a model with hisp as the predictor
lm(fev1 ~ townabbr, data = CHS_data)%>%
  summary()
```

None of the p-value for the slopes are significant. The p-value from the F-test is not significant. 

Here are some predictors that I suspect may be confounding:

* Pollutants
* Town Abbr

So, I'll create a subset of each town, and then build a model for each subset. 

```{r}
SA_subset <- CHS_data%>%filter(townabbr == "SA")
SD_subset <- CHS_data%>%filter(townabbr == "SD")
RV_subset <- CHS_data%>%filter(townabbr == "RV")
GL_subset <- CHS_data%>%filter(townabbr == "GL")
ML_subset <- CHS_data%>%filter(townabbr == "ML")
UP_subset <- CHS_data%>%filter(townabbr == "UP")
AN_subset <- CHS_data%>%filter(townabbr == "AN")
LB_subset <- CHS_data%>%filter(townabbr == "LB")

SA_model <- (lm(fev1 ~ hisp, data = SA_subset)%>%summary())
SD_model <- (lm(fev1 ~ hisp, data = SD_subset)%>%summary())
RV_model <- (lm(fev1 ~ hisp, data = RV_subset)%>%summary())
GL_model <- (lm(fev1 ~ hisp, data = GL_subset)%>%summary())
ML_model <- (lm(fev1 ~ hisp, data = ML_subset)%>%summary())
UP_model <- (lm(fev1 ~ hisp, data = UP_subset)%>%summary())
AN_model <- (lm(fev1 ~ hisp, data = AN_subset)%>%summary())
###AN_model is significant!! 
LB_model <- (lm(fev1 ~ hisp, data = LB_subset)%>%summary())
###LB_model is significant!! 
```

Let's look at the AN_model further.



**Descriptive statistics:**

```{r}
par(mfrow = c(2,2))
plot(fev1 ~ age, data = CHS_data)
plot(fev1 ~ weight, data = CHS_data)
plot(fev1 ~ bmi, data = CHS_data)
plot(fev1 ~ height, data = CHS_data)

```

```{r}
# CHS_data$College <- ifelse(CHS_data$educ %in% c(1,2,3), "No College", "Some College")

CHS_data %>%
  ggplot(aes(x=age, y=fev1, group=as.factor(race), color=as.factor(race))) +
  geom_point() +
  geom_smooth(method="glm")
# 
lm(fev1 ~ factor(race) + age + factor(obesity) + factor(male), data = CHS_data)%>%summary()
```


```{r}
boxplot(fev1~race, data = CHS_data)
```

It doesn't matter what your BMI is. It matters if you're obese. (Use the obesity column in the model. Include 

Don't include height + weight and bmi, because they're so highly correlated! 

There's a trend in parental education, so include in the model. 

Obesity captures BMI, height, and weight. 

**Potential Issues:**

The majority of the sample is caucasian. We should acknowledge this. 






