---
title: "CHS - Logistic Regression"
author: "Abigail Seeger"
date: "7/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, message = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
```

Read in the data. 

```{r}
CHS_data <- read.csv("~/LA's BEST/CHS_Poster/CHS_cohortE_final_subset.csv")
```

Convert the necessary columns to be factors.

```{r}
CHS_data$asthma <- factor(CHS_data$asthma, levels = c(0, 1), labels = c("No Asthma", "Asthma"))
CHS_data$hisp <- factor(CHS_data$hisp)
CHS_data$townabbr <- factor(CHS_data$townabbr)
CHS_data$sex <- factor(CHS_data$male, levels = c(0, 1), labels = c("Female", "Male"))
CHS_data$educ <- factor(CHS_data$educ, levels = c(1, 2, 3, 4, 5), labels = c("No HS", "HS", "Some College", "4-Year Degree", "Some post-graduate"))
CHS_data$wheeze <- factor(CHS_data$wheeze, levels = c(0, 1), labels = c("No Wheeze", "Wheeze"))
CHS_data$obesity <- factor(CHS_data$obesity, levels = c(TRUE, FALSE), labels = c("Obese", "Not Obese"))
```

Build a model to predict the occurence of asthma.

The baseline model will have the following predictors:

*Sex
*Age
*Obesity
*Race

and 

*Town Abbreviation

Add a note: EC is significant when it is the lone predictors. But, it becomes not-significant when we start adjusting. The association becomes larger, but it becomes less-significant. 

(This is similar with the FEV1 model.)

```{r}
CHS_data$townabbr <- relevel(factor(CHS_data$townabbr), ref = "SA")
CHS_remove <- filter(CHS_data, CHS_data$hisp %in% c("Hispanic", "Non-Hispanic"))

### Ask about whether to include wheeze
final_model <- glm(asthma ~ male + age + obesity + race + townabbr + educ + hisp + ec, family = "binomial", data = CHS_data)



hisp_data <- CHS_data%>%
  filter(hisp == "Hispanic")

nonhisp_data <- CHS_data%>%
  filter(hisp =="Non-Hispanic")

### hisp model

glm(asthma ~ male + age + obesity + race + townabbr + educ + ec, family = "binomial", data = hisp_data)%>%summary()

### non-hisp model


glm(asthma ~ male + age + obesity + race + townabbr + educ + ec, family = "binomial", data = nonhisp_data)%>%summary()

```


exp : X times as likely
1 - : X times less/more likely

Explanation for gender and age:




```{r}
missing_data <- filter(CHS_data, CHS_data$hisp == "Unknown or Missing")
glm(asthma ~ male + age + obesity + race + townabbr + educ + wheeze + ec, family = "binomial", data = missing_data)%>%summary()

```

```{r}
CHS_data%>%
  group_by(hisp)%>%
  summarize(mean(ec))
```

```{r}
final_model <- glm(asthma ~ male + age + obesity + race + townabbr + educ  + ec, family = "binomial", data = CHS_data)

predict(final_model, CHS_data)

```

