---
title: "CHS Regression and Logistic Regression"
author: "Abigail Seeger"
date: "6/29/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, message = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
```

Read in the data. 

```{r}
CHS_data <- read.csv("~/LA's BEST/CHS_Poster/CHS_cohortE_final_subset.csv")
```

Based on previous investigations, we have chosen to include the following predictors in the model:

This is the "base line" model with the predictors that are added no matter what. 

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race), data = CHS_data)%>%summary()
```

Now, try adding the pollutants one by one:

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + nitrate, data = CHS_data)%>%summary()

```

Nitrate is marginally significant. Don't include in the model. 

Now, we're adding the following predictors to the baseline model, one by one, to determine whether they should be included in the model:

*educ
*HouseBuilt
*BaseGasstove
*BasePets
*ETS_base

**Included:**

*educ
*BasePets
*townabbr

**Not included:**

*HomeBuilt 
*BaseGasstove
*ETS_base


# educ

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(townabbr), data = CHS_data)%>%summary()
```
# Basepets

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(BasePets), data = CHS_data)%>%summary()
```

# townabbr

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(townabbr) + sulfate, data = CHS_data)%>%summary()

lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race)  + sulfate, data = CHS_data)%>%summary()
```

Relevel by "UP" (Upland) in order to get significant p-values for the neighborhoods. This tells the model to use UP as the baseline. 

```{r}
CHS_data$townabbr <- relevel(factor(CHS_data$townabbr), ref = "UP")
```

Rebuild the model:

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + townabbr, data = CHS_data)%>%summary()
```

# HomeBuilt

```{r}
### Note that gas stoves and year home built seem related
table(CHS_data$BaseGasstove, CHS_data$HomeBuilt)

lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(HomeBuilt), data = CHS_data)%>%summary()

```

Relevel the data by "Unknown or Missing" to see if anything becomes significant.

```{r}
CHS_data$HomeBuilt <- relevel(factor(CHS_data$HomeBuilt), ref = "Unknown or Missing")
```

Rebuild the model.

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(HomeBuilt), data = CHS_data)%>%summary()
```
# BaseGasstove

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(BaseGasstove), data = CHS_data)%>%summary()
```

# ETS_Base

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(townabbr) + factor(ETS_base), data = CHS_data)%>%summary()
```


# Test Pollutants

*pm25
*sulfate
*nitrate
*ec
*dust

```{r}
lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(townabbr) + pm25 + nitrate + sulfate, data = CHS_data)%>%summary()

lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(townabbr) + sulfate, data = CHS_data)%>%summary()
```
**Included:**

*educ
*BasePets
*townabbr

```{r}
# CHS_data$SA <- ifelse(CHS_data$townabbr == "SA", "SA", "Other")
### Pick the "less air polluted" town as a reference
CHS_data$townabbr <- relevel(factor(CHS_data$townabbr), ref = "SA")
final_model <- lm(fev1 ~ factor(male) + age + factor(obesity)  + factor(townabbr) + pm25 + factor(educ) + factor(race), data = CHS_data)
final_model
```
```{r}
CHS_data%>%
  group_by(townabbr)%>%
  summarize(mean = mean(fev1, na.rm = TRUE))
```



```{r}
hisp_data <- filter(CHS_data, CHS_data$hisp == "Hispanic")
nonhisp_data <- filter(CHS_data, CHS_data$hisp == "Non-Hispanic")

nonhisp_data$educ <- relevel(factor(nonhisp_data$educ), ref = "5")
hisp_data$educ <- relevel(factor(hisp_data$educ), ref = "5")

```

```{r}
### Pick the "less air polluted" town as a reference
CHS_data$townabbr <- relevel(factor(CHS_data$townabbr), ref = "SA")


lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(townabbr) + pm25 + factor(educ) , data = hisp_data)%>%summary()

lm(fev1 ~ factor(male) + age + factor(obesity) + factor(race) + factor(townabbr) + pm25 + factor(educ) , data = nonhisp_data)%>%summary()

```

1. Ask JP how to tackle "unknown or missing" column in race and hisp columns.

2. Is it okay to have race and ethnicity in the model at the same time?
3. How to check the assumptions of the model using R?

Next time, check the residuals of the model. 


Ethnicity is a modifier. If you don't take into account ethnicity, pm25 is significant. But, the effect is changed once you 

When stratified:

pm25 becomes not significant, but the effect the same. This is probably due to the smaller sample sizes of the stratified models. 

Whatever you found in the main model was replicated in the two stratified models. 

```{r}
### Predict the fev1 levels from the CHS data using our final model
predictions <- predict(lm(fev1 ~ factor(male) + age + factor(obesity)  + factor(townabbr) + pm25 + factor(educ) + factor(race), data = CHS_data), CHS_data)
### Extract the actual fev1 levels from the data set
actual <- CHS_data$fev1
### Plot the actual versus predicted values
plot(predictions ~ actual,
     xlab = "Actual Fev1 Values",
     ylab = "Predicted Fev1 Values")
### Add a line where a "perfect" prediction would be 
abline(coef = c(0,1), col = "red", lty = 2)
### Add the line of best fit between actual and predicted values
abline(lm(predictions ~ actual), col = "blue", lty = 3)
legend(2050, 4650, legend = c("y = x", "Line of Best Fit"),col = c("red", "blue"), lty = c(2,3))
```


```{r}
tiff("ModelDiagnostics.tiff", units="in", width=5, height=5, res=500)
par(mfrow = c(2,2))
plot(final_model)
dev.off()
```

