---
title: "CHS Spatial"
author: "Abigail Seeger"
date: "7/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# {.tabset}  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup {.tabset}

### Packages and Data

Install the following packages and set the directory where data are located:

```{r pkgs, message=F, warning=F}
library(dplyr)
library(ggplot2)
library(leaflet) # plotting spatial data
library(htmlwidgets) # to save html maps that are interactive
library(sf) # handle simple features objects
library(ggmap) # for querying google API for geocoding

```


Now let's import the CHS data (which includes latitude and longitude coordinates and pollutants and outcomes) and map them.

```{r pmdat}
# pm25 = read.csv("~/LA's BEST/LAsBEST/google-drive/week03/3Thurs/pm25_ca_2018.csv")
# pm25.sites = read.csv("~/LA's BEST/LAsBEST/google-drive/week03/3Thurs/pm25_sites.csv")
# pm25 %>% head()
# # pm25.sites %>% head()

CHS_data <- read.csv("~/LA's BEST/CHS_Poster/CHS_cohortE_final_subset.csv")


```

Visualize the sulfate levels for the children in the study. 

```{r pm-maps}
sulfate.pal = colorNumeric(c('darkblue', "blue",'purple','red'),
                        domain=CHS_data$sulfate)
CHS_data %>% 
  st_as_sf(coords=c('longitude','latitude'), crs=4326) %>% 
  leaflet() %>% 
  addProviderTiles('CartoDB.Positron') %>% 
  addCircles(label=~paste0(pm25, ' ug/m3'), color=~sulfate.pal(sulfate),
             opacity=1, fillOpacity=1, radius=500) %>%
  addLegend('bottomleft', pal=sulfate.pal, values=CHS_data$sulfate,
            title='Sulfate (ug/m3)', opacity=1)

```

Now, look at BMI. (Melissa created the "obese" map, which basically shares the same information.)

```{r pm-maps}
asthma.pal = colorFactor(c('green','red'),
                        domain=CHS_data$asthma)
CHS_data %>% 
  st_as_sf(coords=c('longitude','latitude'), crs=4326) %>% 
  leaflet() %>% 
  addProviderTiles('OpenStreetMap') %>% 
  addCircles(label=~paste0(asthma), color=~asthma.pal(asthma),
             opacity=0.5, fillOpacity=0.5, radius=100) %>%
  addLegend('bottomleft', pal=asthma.pal, values=CHS_data$asthma,
            title='Asthma', opacity=0.5)

```



```{r}
pm25.pal = colorNumeric(c('darkblue','blue','purple', "red", "red"),
                        domain=CHS_data$pm25)
fev1.pal = colorNumeric(c('darkblue','blue','purple', "red", "red"),
                        domain=CHS_data$fev)
dust.pal = colorNumeric(c('darkblue','blue','purple', "red", "red"),
                        domain=CHS_data$dust)
sulfate.pal = colorNumeric(c('darkblue','blue','purple', "red", "red"),
                        domain=CHS_data$sulfate)

map <- leaflet(CHS_data) %>%
  # Base groups
  addTiles(group = "OSM (default)") %>%
  addProviderTiles(providers$Stamen.Toner, group = "CartoDB.Positron") %>%
  addProviderTiles(providers$Stamen.Terrain, group = "Terrain") %>%
  # Overlay groups
  addCircles(color=~pm25.pal(pm25)) %>%
  addCircles(color=~fev1.pal(fev1)) %>%
  addCircles(color=~dust.pal(dust)) %>%
  addCircles(color=~sulfate.pal(sulfate)) %>%
  # Layers control
  addLayersControl(
    baseGroups = c("OSM", "Carto.DB", "Terrain"),
    overlayGroups = c("Pm2.5", "Fev1", "Dust", "Sulfate"),
    options = layersControlOptions(collapsed = FALSE)
  )
map

```



```{r}
CHS_data$educ <- factor(CHS_data$educ,
                        levels = c(1, 2, 3, 4, 5),
                        labels = c("Didn't graduate high school",
                                   "Graduated high school",
                                   "Some college",
                                   "Graduated college",
                                   "Some graduate level"))


CHS_data$educ2 <- ifelse(CHS_data$educ %in% c("Graduated college", "Some graduate level", "Some College"), "At least some college", "At most graduated high school")
```

Look at education:

```{r pm-maps}
education.pal = colorFactor(c('red', "orange",'yellow','green', "blue"),
                        domain=CHS_data$educ)
CHS_data %>% 
  st_as_sf(coords=c('longitude','latitude'), crs=4326) %>% 
  leaflet() %>% 
  addProviderTiles('CartoDB.Positron') %>% 
  addCircles(label=~educ, color=~education.pal(educ),
             opacity=1, fillOpacity=1, radius=500) %>%
  addLegend('bottomleft', pal=education.pal, values=CHS_data$educ,
            title='Education', opacity=1)

education.pal2 = colorFactor(c('blue', "red"),
                        domain=CHS_data$educ2)
CHS_data %>% 
  st_as_sf(coords=c('longitude','latitude'), crs=4326) %>% 
  leaflet() %>% 
  addProviderTiles('CartoDB.Positron') %>% 
  addCircles(label=~educ2, color=~education.pal2(educ2),
             opacity=1, fillOpacity=1, radius=50) %>%
  addLegend('bottomleft', pal=education.pal2, values=CHS_data$educ2,
            title='Education', opacity=1)

```
